---
title: "Provide PubMed sqlite/tibble/data.table datasets for AnnotationHub"
author: "Koki Tsuyuzaki"
graphics: no
package: AHPubMedDbs
output:
    BiocStyle::html_document:
        toc_float: true
vignette: >
    %\VignetteIndexEntry{Provide PubMed sqlite/tibble/data.table datasets for AnnotationHub}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
    %\VignetteDepends{AnnotationHub}
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Authors**: `r packageDescription("AHPubMedDbs")[["Author"]] `<br />
**Last modified:** `r file.info("pubmed.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Fetch PubMed tibble datasets from `AnnotationHub`

The `AHPubMedDbs` package provides the metadata for all PubMed datasets
, which is preprocessed as tibble format and saved in
`r Biocpkg("AnnotationHub")`.
First we load/update the `AnnotationHub` resource.

```{r load-lib, message = FALSE}
library(AnnotationHub)
ah <- AnnotationHub()
```

Next we list all PubMed entries from `AnnotationHub`.

```{r list-PubMedDb}
query(ah, "PubMed")
```

We can confirm the metadata in AnnotationHub in Bioconductor S3 bucket
with `mcols()`.

```{r confirm-metadata}
mcols(query(ah, "PubMed"))
```

We can retrieve only the PubMedDb tibble files as follows.

```{r query-mouse}
qr <- query(ah, c("PubMedDb"))
# pubmed_tibble <- qr[[1]]
```

# Session information {.unnumbered}
```{r sessionInfo, echo=FALSE}
sessionInfo()
```